Ecological network control

### 2018-06-03 paper/cover-letter.tex
the senior editor is David Gibson

We are thankful to the senior and associate editors, Prof. James Ross and Prof. Nicole Rafferty, and two anonymus reviewers for the insightful comments to improve the manuscript. 
We are also grateful for the opportunity to resubmit. 
In the attached document, you can find a detailed response to each of their comments. 
For your benefit, we also summarise here the main changes we have made to our manuscript.

>>>>

We are thankful to the senior and associate editors, Prof.\ David Gibson and Prof.\ Nicole Rafferty, and two anonymous reviewers for the insightful comments to improve the manuscript. 
We are also grateful for the opportunity to resubmit. 
In the attached document, you can find a detailed response to each of their comments. 
For your benefit, we also summarise here the main changes we have made to our manuscript.
